---
title: "Exploratory Data Analysis"
author: "Mandalika Sai Prerana"
format:
  html:
    embed-resources: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(stringr)
library(janitor)
library(tidyr)
library(dplyr)
library('tidyverse')
```

```{r}
# INSERT CODE TO READ THE DATA FILES 
df <- read.csv("../../data/01-modified-data/combined_data_clean.csv")
tibble_df <- as_tibble(df)

tibble_df[1, "ADHD.Index"] <- 100

tibble_df[34, "ADHD.Index"] <- 150
tibble_df
```

```{r}
null_counts <- tibbe_df %>%
  summarise_all(~sum(is.na(.)))
tibble_df
```

```{r}
tibble_df <- tibble_df %>%
  mutate(Secondary.Dx = ifelse(Secondary.Dx == 'pending', NaN, Secondary.Dx))
```


```{r}
tibble_df
```
```{r}
my_tibble <- my_tibble %>%
  select_if(~!any(is.na(.)))
```

```{r}
#check for and remove outliers
# Create a scatter plot to visualize outliers
ggplot(data = tibble_df, aes(x = 1, y = ADHD.Index )) +
  geom_point()
```

```{r}
# Create a box plot to visualize outliers
ggplot(data = tibble_df, aes(x = "", y = ADHD.Index)) +
  geom_boxplot()
```
```{r}
correlation_matrix <- cor(select(tibble_df, where(is.numeric)))
correlation_matrix
```

```{r}
ggplot(data, aes(x = Variable1, y = Variable2)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)  # Add a linear regression line
```
_Use R to answer the following questions._

In a certain large city, 34% of the adult population has a college degree. In a random sample of size  800,

a. What is the exact probability that between 250 and 290 adults have a college degree?

Hint: ( _Exact distribution:_ B(800,.34).) 

b. What is the approximate normal distribution of the fraction of adults in the sample with a college degree?
_The fraction is a sample mean. What does the Central Limit Theorem say?_ (Answer (i)-(iii) by hand)

* _for each person in the sample the question "Do you have a college degree?" is like a Bernoulli r.v., B(1,p)._

(i). _What is p?_ 

(ii). _what are the mean and standard deviation of a single result?_ 

(iii). What is the distribution of the sample fraction, that is sample mean?


(iv). What is the probability, if the approximate normal distribution is used? (use R). Compare ther result with the exact value.

* The sample fraction has an approximate normal distribution with mean $p$ and standard deviation $\sqrt{\frac{p(1-p)}{n}}$.

* The sample count (number of adults with college degree in the sample) has an approximate normal distribution with mean $np$ and standard deviation $\sqrt{np(1-p)}$. 



# Problem-2

Repeat the Same likelihood example(Example 1) done for Poisson distribution in class for an exponential distribution.

a. Write a function to get the likelihood function for data from exponential distribution.


b. Generate a random sample of size 5 from an exponential distribution: Let's say the variable named "X.2".


c. Compute the likelihoods(using X.2) for a range of lambda(t) and plot them: Then find for which value the likelihood is maximized?


d. Plot the same thing for log likelihood: 

e. Repeat this 10 times

* 10 random samples with the same lambda
* plot each log-likelihood in the same plot
* what can you say about log likelihoods according to the plot?  Does it have to do with the sample size we chose?


# Problem-3: Optional 

`Don't need to submit anything for this one`

Consider the probability distribution with density
$$
f(x|\theta) = \begin{cases}
\theta x^{\theta - 1} \quad (0 \le x \le 1) \\
0 \quad \text{otherwise}
\end{cases}
$$
where $\theta > 0$ is unknown. 

Find a formula for the method-of-moments estimate for $\theta$.

